InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-19 paper.tex
Apply rephrasings from Roschtbraten
Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

As for text processors, we evaluated on three different methods of augmenting the text. The first approach is to replace every white-space in a given text, by two white-spaces. The second approach is to add some typos to the texts. This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human. The typos include mistakes, like not hitting the right key, but a key close to the one, that should have been hit instead. This results in typos close to real typos by humans. The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english. As translator are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.

>>>>

As for text processors, we evaluated three different methods of augmenting generated texts. The first approach was to replace every white-space in a given text by two white-spaces. The second approach was to add some typos to the texts. This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human. The typos include mistakes, like hitting a wrong key, which is close to the right one. This results in typos often created by humans. The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english. As translator are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.
